---
title: "Homework 1"
output: pdf_document
date: "2025-06-26"
author: "Ma Xinyuan"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
iowa.df<-read.csv("data/Iowa.csv", sep = ';', header=T)
library(DAAG)
```

## Problem 1.

b. It has 33 rows and 10 colomns.
```{r}
dim(iowa.df)
```

c.
```{r}
colnames(iowa.df)
```

d.
```{r}
iowa.df[5, 7]
```

e.
```{r}
iowa.df[2, ]
```

## Problem 2.

a.
```{r}
vector1 <- c("5", "12", "7", "32")
max(vector1)
sort(vector1)
```
This is because string comparison is done based on lexicographical order, and "1" < "3" < "5" < "7".
```{r, eval = FALSE}
sum(vector1)
```
This command is error. This is because a string is a character-type data, whereas the sum() function can only perform addition on numeric data.

b. 
```{r, eval = FALSE}
vector2 <- c("5", 7, 12)
vector2[2] + vector2[3]
```
The second command is a error. This is because vector2[1] is a character type ("5"), so R will attempt to convert all elements to character type. However, character data cannot be directly added together.
```{r}
dataframe3 <- data.frame(z1 = "5", z2 = 7, z3 = 12)
dataframe3[1, 2] + dataframe3[1, 3]
```
The data types in dataframe are not necessarily same. Therefore it's sum of two numeric data. 
```{r}
list4 <- list(z1 = "6", z2 = 42, z3 = "49", z4 = 126)
list4[[4]] + list4[[2]]
```
```{r, eval = FALSE}
list4[4] + list4[2]
```
This command is error. In list, [[]] extracts a single element directly returns the original type of the element, while [] returns data type of list.

## Problem 3.
a. 
```{r}
sequence1 = seq(from = 1, to = 10000, by = 372)
sequence2 = seq(from = 1, to = 10000, by = (10000 - 1) / (50 - 1))
length(sequence2)
```

b.
```{r}
rep(1 : 3, times = 3)
rep(1 : 3, each = 3)
```
The first command repeat the whole vector several times, while the second command repeat each element in the vector several times.

## MB.Ch1.2.
```{r}
new_orings <- orings[c(1, 2, 4, 11, 13, 18), ]
plot(new_orings$Temperature, new_orings$Total, xlab = "Temperature", ylab = "Total Incidents", 
     main = "Total Incidents vs Temperature (partical data)")
plot(orings$Temperature, orings$Total, xlab = "Temperature", ylab = "Total Incidents", 
     main = "Total Incidents vs Temperature (full data)")
```

## MB.Ch1.4.
(a).
```{r}
str(ais)
any(is.na(ais))
```
(b).
```{r}
table(ais$sport, ais$sex)
```
In T_sprnt and W_Polo, there are large imbalance.

## MB.Ch1.6.
```{r}
elevation <- c(217, 254, 248, 254, 253, 227, 178, 207, 217)
area <- c(24387, 5374, 4624, 2247, 1353, 1223, 1151, 755, 657)
names <- c("Winnipeg", "Winnipegosis", "Manitoba", "SouthernIndian", "Cedar", "Island", "Gods", "Cross", "Playgreen")
Manitoba.lakes <- data.frame(elevation, area)
rownames(Manitoba.lakes) <- names
```
(a).
```{r}
attach(Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
# NB: Doubling the area increases log2(area) by 1.0
text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2)
title("Manitoba's Largest Lakes")
```
Each point represents a lake. The label is its name, the number near it is the real area and y-axis is the area taking logarithm of 2.
(b).
```{r}
plot(area ~ elevation, pch=16, xlim=c(170,280), ylog=T)
text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)
text(area ~ elevation, labels=area, pos=2, ylog=T)
title("Manitoba's Largest Lakes")
```

## MB.Ch1.7.
```{r}
dotchart(area, rownames(Manitoba.lakes))
title(main = "Area of lakes", sub = "On a linear scale")
dotchart(log2(area), rownames(Manitoba.lakes))
title(main = "Area of lakes", sub = "On a logarithmic scale")
```

## MB.Ch1.8.
```{r}
sum(Manitoba.lakes$area)
```